---
title: "Association RM Code"
author: "Prasenjeet Madhav Gadhe"
date: "2023-02-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Packages Installing
```{r}
#install.packages("arules")
## For arulesViz to work on R version 3.5.x, you will
## need to first go through an installation of RTools. 
## See HOW TO above.
## Next - once the RTools exe has been downloaded and installed
## per the instructions, then, do these install.packages here in RStudio:
#install.packages("TSP")
#install.packages("data.table")
## NOTE: If you are asked if you want to INSTALL FROM SOURCE - click YES!
#install.packages("arulesViz", dependencies = TRUE)
## IMPORTANT ## arules ONLY grabs rules with ONE item on the right
## install.packages("sp")
## NOTE R V3.5.0 does not use the older
## datasets packages
## install.packages("datasets.load") - not used here
## install.packages("ggplot2") - not used here

## install.packages("dplyr", dependencies = TRUE)
 install.packages("purrr", dependencies = TRUE)
## install.packages("devtools", dependencies = TRUE)
## install.packages("tidyr")

```


Calling Libraries
```{r}
library(viridis)
library(arules)
library(TSP)
library(data.table)
#library(ggplot2)
#library(Matrix)
library(tcltk)
library(dplyr)
#library(devtools)   # for now commetted
library(purrr)
library(tidyr)
## DO THIS ONCE
## FIRST - you MUST register and log into github
## install_github("mhahsler/arulesViz")
## RE: https://github.com/mhahsler/arulesViz

##############
## IF YOUR CODE BREAKS - TRY THIS
##
## Error in length(obj) : Method length not implemented for class rules 
## DO THIS: 
## (1) detach("package:arulesViz", unload=TRUE)
## (2) detach("package:arules", unload=TRUE)
## (3) library(arules)
## (4) library(arulesViz)
###################################################################

## To see if you have tcltk run this on the console...
# capabilities()["tcltk"]
library(arulesViz)

```


## YOUR working dir goes here...
#setwd("C:/Users/profa/Documents/RStudioFolder_1/DrGExamples/ANLY501")


###################################
## Example 1: Kumar's Beer Example
##
## Dataset: https://drive.google.com/file/d/1BvU3iXtrwxfjBsRShaDgI-Ldh7Y3XSEn/view?usp=sharing
## KumarGroceriesAS_Transactions
##
## ## Dataset:
## HealthyBasket
## https://drive.google.com/file/d/1qaWSTwjrj7tNB43zLss9KC_ecJKp6W4g/view?usp=sharing
###################################################

Reading the File
```{r}
Musk_df <- read.transactions("Musk_Cleaned_transactions.csv",
                           rm.duplicates = FALSE, 
                           format = "basket",  ##if you use "single" also use cols=c(1,2)
                           sep=",",  ## csv file
                           cols=NULL) ## The dataset HAS row numbers
inspect(Musk_df)
```

##### Use apriori to get the RULES
```{r}
FrulesK = arules::apriori(Musk_df, parameter = list(support=.09,                   ##We come up with certain support by guesss
                                                 confidence=.005, minlen=1))
inspect(FrulesK)
```
## Plot of which items are most frequent
```{r}
itemFrequencyPlot(Musk_df, topN=20, type="absolute")
```
## Sort rules by a measure such as conf, sup, or lift
```{r}
SortedRulesK <- sort(FrulesK, by="confidence", decreasing=TRUE)
inspect(SortedRulesK[1:10])
(summary(SortedRulesK))
```

## Selecting or targeting specific rules  LHS
### Looking for Revenue association
```{r}
## Selecting rules with LHS specified
CarrotRules <- apriori(data=Musk_df,parameter = list(supp=.01, conf=.01, minlen=2),
                     appearance = list(default="rhs", lhs="revenue"),
                     control=list(verbose=FALSE))
CarrotRules <- sort(CarrotRules, decreasing=TRUE, by="support")
inspect(CarrotRules[1:20])
```

### Looking for Recession association
```{r}
## Selecting rules with LHS specified
CarrotRules <- apriori(data=Musk_df,parameter = list(supp=.01, conf=.01, minlen=2),
                     appearance = list(default="rhs", lhs="recession"),
                     control=list(verbose=FALSE))
CarrotRules <- sort(CarrotRules, decreasing=TRUE, by="support")
inspect(CarrotRules[1:20])
```

### Top 15 Rules w.r.t. Cnofidence
```{r}
SortedRulesK <- sort(FrulesK, by="lift", decreasing=TRUE)
inspect(SortedRulesK[1:15])
(summary(SortedRulesK))
```














## Visualize
## tcltk
```{r}
subrulesK <- head(sort(SortedRulesK, by="lift"),10)
plot(subrulesK)

plot(subrulesK, method="graph", engine="interactive")
```


####################################################
## Example 2: Healthy Food Transaction Data
##
## HERE IS THE DATA - but you should make your own dataset!
## https://drive.google.com/file/d/1qaWSTwjrj7tNB43zLss9KC_ecJKp6W4g/view?usp=sharing
##
##############################################################
```{r}
Foods <- read.transactions("HealthyBasketData.csv",
                             rm.duplicates = FALSE, 
                             format = "basket",  ##if you use "single" also use cols=c(1,2)
                             sep=",",  ## csv file
                             cols=NULL) ## The dataset has no row numbers
inspect(Foods)
```
##### Use apriori to get the RULES
```{r}
Frules = arules::apriori(Foods, parameter = list(support=.35, 
                                          confidence=.5, minlen=2))
inspect(Frules)
```

## Plot of which items are most frequent
```{r}
itemFrequencyPlot(Foods, topN=20, type="absolute")
```


## Sort rules by a measure such as conf, sup, or lift
```{r}
SortedRules <- sort(Frules, by="confidence", decreasing=TRUE)
inspect(SortedRules[1:10])
(summary(SortedRules))
```


## Selecting or targeting specific rules  RHS
```{r}
ChocRules <- apriori(data=Foods,parameter = list(supp=.001, conf=.01, minlen=2),
                     appearance = list(default="lhs", rhs="chocloate"),
                     control=list(verbose=FALSE))
ChocRules <- sort(ChocRules, decreasing=TRUE, by="confidence")
inspect(ChocRules[1:4])

## Selecting rules with LHS specified
CarrotRules <- apriori(data=Foods,parameter = list(supp=.001, conf=.01, minlen=2),
                     appearance = list(default="rhs", lhs="carrot"),    ## To force any set between Left or Right
                     control=list(verbose=FALSE))
CarrotRules <- sort(CarrotRules, decreasing=TRUE, by="support")
inspect(CarrotRules[1:4])
```

## Visualize
## tcltk

```{r}
subrules <- head(sort(SortedRulesK, by="confidence"),10)
plot(subrules)

#plot(subrules, method="graph", engine="interactive")
plot(subrules, method="graph", engine="htmlwidget")
```